\documentclass[12pt]{exam}

% essential packages
\usepackage{fullpage} % margin formatting
\usepackage{enumitem} % configure enumerate and itemize
\usepackage{amsmath, amsfonts, amssymb, mathtools} % math symbols
\usepackage{xcolor, colortbl} % colors, including in tables
\usepackage{makecell} % thicker \Xhline in table
\usepackage{graphicx} % images, resizing

\usepackage[dvipsnames]{xcolor}
\usepackage[framemethod=tikz]{mdframed}

\newcommand{\commentsection}[1]{
  \begin{mdframed}[roundcorner=10pt,leftmargin=1cm,%
                     rightmargin=1cm,backgroundcolor=SkyBlue!20,%
                     innertopmargin=\baselineskip,%
                     skipabove=\baselineskip,%
                     skipbelow=\baselineskip]
  #1
  \end{mdframed}
}

% sometimes needed packages
\usepackage{hyperref} % hyperlinks
% \hypersetup{colorlinks=true, urlcolor=blue}
% \usepackage{logicproof} % natural deduction
% \usepackage{tikz} % drawing graphs
% \usetikzlibrary{positioning}
% \usepackage{multicol}
% \usepackage{algpseudocode} % pseudocode

% paragraph formatting
\setlength{\parskip}{6pt}
\setlength{\parindent}{0cm}

% newline after Solution:
\renewcommand{\solutiontitle}{\noindent\textbf{Solution:}\par\noindent}


% less space before itemize/enumerate
\setlist{topsep=0pt}

% creates \filcl to grey out cells for groupwork grading
\newcommand{\filcl}{\cellcolor{gray!25}}

% creates \probnum to get the problem number
\newcounter{probnumcount}
\setcounter{probnumcount}{1}
\newcommand{\probnum}{\arabic{probnumcount}. \addtocounter{probnumcount}{1}}

% use roman numerals by default
\setlist[enumerate]{label={(\roman*)}}

% creates custom list environments for grading guidelines, question parts
\newlist{guidelines}{itemize}{1}
\setlist[guidelines]{label={}, left=0pt .. \parindent, nosep}
\newlist{gwguidelines}{enumerate}{1}
\setlist[gwguidelines]{label={(\roman*)}, nosep}
\newlist{qparts}{enumerate}{2}
\setlist[qparts]{label={(\alph*)}}
\newlist{qsubparts}{enumerate}{2}
\setlist[qsubparts]{label={(\roman*)}}
\newlist{stmts}{enumerate}{1}
\setlist[stmts]{label={(\roman*)}, nosep}
\newlist{pflist}{itemize}{4}
\setlist[pflist]{label={$\bullet$}, nosep}
\newlist{enumpflist}{enumerate}{4}
\setlist[enumpflist]{label={(\arabic*)}, nosep}

\printanswers

\newcommand{\prevhwnum}{6}
\newcommand{\hwnum}{6}

\begin{document}
\section*{Grading of Groupwork \prevhwnum{}}
Using the solutions and Grading Guidelines, grade your Groupwork \prevhwnum{} Problems:
\begin{itemize}
	\item Use the table below to grade your past Groupwork submission and calculate scores.
	\item While grading, mark up your past submission. Include this with the table when you submit your grading.
	\item Write whether your submission achieved each rubric item. If it didn't achieve one, say why not.
	\item For extra credit, write positive comment(s) about your work.
	\item You don't have to redo problems correctly, but it is recommended!
	\item See ``All About Groupwork" on Canvas for more detailed guidance, and what to do if you change groups.
\end{itemize}

\begin{center}
	\resizebox{\textwidth}{!}{\begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c |}
			\hline
			          & (i)    & (ii)   & (iii)  & (iv)   & (v)    & (vi)   & (vii)  & (viii) & (ix)   & (x)    & (xi)   & Total:            \\
			\hline
			Problem 1 & 4      & 4      & 4      & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \hspace{1cm}12/12 \\
			\hline
			Problem 2 & 2      & 0      & 0      & 2      & 2      & 2      & 0      & 3      & \filcl & \filcl & \filcl & \hspace{1cm}11/18 \\
			\Xhline{1.25pt}
			Total:    & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \filcl & \hspace{1cm}23/30 \\
			\hline
		\end{tabular}}
\end{center}

\section*{Comments}
\commentsection{I don't really get the second problem completely. However, I figured out the first problem on my own, kuddos to me.}


\subsection*{\probnum Multiple Multiples [12 points]}
Let $a,b\in \mathbb{Z}$. Show that $7a - 8b$ is a multiple of 5 if and only if $19a - 21b$ is a multiple of 5.

\begin{solution}
	Let $a,b\in \mathbb{Z}$. We want to show that $7a - 8b$ is a multiple of 5 if and only if $19a - 21b$ is a multiple of 5.\\
	In other words, we want to show that $7a - 8b \equiv 0 \pmod{5}$ if and only if $19a - 21b \equiv 0 \pmod{5}$.\\
	i.e. in logic notation, we want to show that $(7a - 8b \equiv 0 \pmod{5}) \iff (19a - 21b \equiv 0 \pmod{5})$.\\
	We will show this by proving both directions of the biconditional.\\
	\begin{tabular}{ll}
		LHS:                                                                           \\
		Assume $7a - 8b \equiv 0 \pmod{5}$                         &                   \\
		$7a - 8b\pmod{5} \equiv 2a-3b\pmod{5} \equiv 0\pmod{5}$    & definition of mod \\
		$2a-3b=5k$ for some $k\in\mathbb{Z}$                       & definition of mod \\
		$2a=5k+3b$                                                 & algebra           \\
		$4a=10k+6b$                                                & algebra           \\
		$19a-21b\pmod{5} \equiv 4a-1b\pmod{5}$                     & definition of mod \\
		$10k+6b-1b\pmod{5} \equiv 10k+5b\pmod{5} \equiv 0\pmod{5}$ & algebra           \\
	\end{tabular}\\
	Therefore, $19a - 21b \equiv 0 \pmod{5}$.\\
	\begin{tabular}{ll}
		RHS:                                                                           \\
		Similarly, assume $19a - 21b \equiv 0 \pmod{5}$            &                   \\
		$19a - 21b\pmod{5} \equiv 4a-1b\pmod{5} \equiv 0\pmod{5}$  & definition of mod \\
		$4a-1b=5k$ for some $k\in\mathbb{Z}$                       & definition of mod \\
		$b=4a-5k$                                                  & algebra           \\
		$7a - 8b\pmod{5} \equiv 7a-8b\pmod{5}\equiv 2a-3b\pmod{5}$ & definition of mod \\
		$2a-3b\pmod{5} \equiv 2a-3(4a-5k)\pmod{5}$                 & substitution      \\
		$2a-3(4a-5k)\pmod{5} \equiv 2a-12a+15k\pmod{5}$            & algebra           \\
		$2a-12a+15k\pmod{5} \equiv -10a+15k\pmod{5}$               & algebra           \\
		$-10a+15k\pmod{5} \equiv 0\pmod{5}$                        & algebra           \\
	\end{tabular}\\
	Therefore, $7a - 8b \equiv 0 \pmod{5}$.\\
	Since we have shown both directions of the biconditional, we have shown that $7a - 8b$ is a multiple of 5 if and only if $19a - 21b$ is a multiple of 5.
\end{solution}

\subsection*{\probnum Rapidly Rising [18 points]}
For this problem, we will say a function $f\colon \mathbb{Z}^+ \to \mathbb{Z}^+$ is ``rapidly rising'' if:
$$ \forall x_1, x_2 \in \mathbb{Z}^+ \ [x_1 < x_2 \to 2f(x_1) < f(x_2)] $$

\begin{qparts}
	\item Prove that $f(x) = 3^x$ is rapidly rising.

	\textbf{Hint:} It may be easier to show $f(x_2) > 2f(x_1)$ than the other way around.

	\item Is a rapidly rising function always one-to-one? Is a one-to-one function from $\mathbb{Z}^+\to\mathbb{Z}^+$ always rapidly rising? Is a one-to-one function (again from $\mathbb{Z}^+\to\mathbb{Z}^+$) always strictly increasing? Briefly explain your answer; a formal proof is not necessary but is encouraged.

	\textbf{Note:} $f\colon\mathbb{N}\to\mathbb{N}$ is strictly increasing if $f(x_1)<f(x_2)$ whenever $x_1<x_2.$
	\item Prove that, for any rapidly rising function $f$, it must \textbf{not} be onto.
\end{qparts}


\begin{solution}
	a) Let $f(x) = 3^x$. We want to show that $f(x)$ is rapidly rising.\\
	Let $x_1, x_2 \in \mathbb{Z}^+$ such that $x_1 < x_2$.\\
	We want to show that $2f(x_1) < f(x_2)$.\\
	We have $f(x_1) = 3^{x_1}$ and $f(x_2) = 3^{x_2}$.\\
	We want to show that $2\cdot 3^{x_1} < 3^{x_2}$.\\
	\textcolor{red}{Use chain of inequalities to show this.}\\
	Since for $f(x)$, the base is 3, thus for every increase in $x$, the value of $f(x)$ is multiplied by 3.\\
	Thus, no matter what the value of $x_1$ is, $3^{x_1}$ will always be less than $3^{x_2}$ for any $x_2 > x_1$.\\
	Therefore, $2\cdot 3^{x_1} < 3^{x_2}$.\\
	Since we have shown that $2f(x_1) < f(x_2)$, we have shown that $f(x) = 3^x$ is rapidly rising.\\
	b) A rapidly rising function is not always one-to-one.\\
	A one-to-one function from $\mathbb{Z}^+\to\mathbb{Z}^+$ is not always rapidly rising.\\
	A one-to-one function from $\mathbb{Z}^+\to\mathbb{Z}^+$ is not always strictly increasing.\\
	A rapidly rising function is not always one-to-one because a rapidly rising function only guarantees that $2f(x_1) < f(x_2)$ for $x_1 < x_2$. It does not guarantee that $f(x_1) \neq f(x_2)$ for $x_1 \neq x_2$.\\
	A one-to-one function from $\mathbb{Z}^+\to\mathbb{Z}^+$ is not always rapidly rising because a one-to-one function only guarantees that $f(x_1) \neq f(x_2)$ for $x_1 \neq x_2$. It does not guarantee that $2f(x_1) < f(x_2)$ for $x_1 < x_2$.\\
	A one-to-one function from $\mathbb{Z}^+\to\mathbb{Z}^+$ is not always strictly increasing because a one-to-one function only guarantees that $f(x_1) \neq f(x_2)$ for $x_1 \neq x_2$. It does not guarantee that $f(x_1) < f(x_2)$ for $x_1 < x_2$.\\
	c) Let $f$ be a rapidly rising function. We want to show that $f$ must not be onto.\\
	A function $f$ is onto if for every $y\in\mathbb{Z}^+$, there exists an $x\in\mathbb{Z}^+$ such that $f(x) = y$.\\
	We will show that $f$ must not be onto by contradiction.\\
	Assume for the sake of contradiction that $f$ is onto.\\
	Since $f$ is onto, for every $y\in\mathbb{Z}^+$, there exists an $x\in\mathbb{Z}^+$ such that $f(x) = y$.\\
	Let $x_1, x_2 \in \mathbb{Z}^+$ such that $x_1 < x_2$.\\
	We have $f(x_1) < f(x_2)$ because $f$ is rapidly rising.\\
	Since $f$ is onto, for every $y\in\mathbb{Z}^+$, there exists an $x\in\mathbb{Z}^+$ such that $f(x) = y$.\\
	Let $y = f(x_2)$.\\
	Since $f$ is onto, there exists an $x\in\mathbb{Z}^+$ such that $f(x) = f(x_2)$.\\
	Since $f$ is one-to-one, $x = x_2$.\\
	Since $x_1 < x_2$, $f(x_1) < f(x_2)$.\\
	This is a contradiction because $f(x_1) < f(x_2)$ but $f(x_1) = f(x_2)$.\\
	\textcolor{red}{Give an example of a function that is rapidly rising but not onto.}\\
	Therefore, $f$ must not be onto.\\
	Since we have shown that $f$ must not be onto, we have shown that for any rapidly rising function $f$, it must not be onto.
\end{solution}


\end{document}
