\documentclass[12pt]{exam}

% essential packages
\usepackage{fullpage} % margin formatting
\usepackage{enumitem} % configure enumerate and itemize
\usepackage{amsmath, amsfonts, amssymb, mathtools} % math symbols
\usepackage{xcolor, colortbl} % colors, including in tables
\usepackage{makecell} % thicker \Xhline in table
\usepackage{graphicx} % images, resizing

% sometimes needed packages
\usepackage{wasysym} % Just used for \smiley{}
\usepackage{hyperref} % hyperlinks
\hypersetup{colorlinks=true, urlcolor=blue}
% \usepackage{logicproof} % natural deduction
% \usepackage{tikz} % drawing graphs
% \usetikzlibrary{positioning}
% \usepackage{multicol}
% \usepackage{algpseudocode} % pseudocode

% paragraph formatting
\setlength{\parskip}{6pt}
\setlength{\parindent}{0cm}

% newline after Solution:
\renewcommand{\solutiontitle}{\noindent\textbf{Solution:}\par\noindent}

% less space before itemize/enumerate
\setlist{topsep=0pt}

% creates \filcl to grey out cells for groupwork grading
\newcommand{\filcl}{\cellcolor{gray!25}}

% creates \probnum to get the problem number
\newcounter{probnumcount}
\setcounter{probnumcount}{1}
\newcommand{\probnum}{\arabic{probnumcount}. \addtocounter{probnumcount}{1}}

% use roman numerals by default
\setlist[enumerate]{label={(\roman*)}}

% creates custom list environments for grading guidelines, question parts
\newlist{guidelines}{itemize}{1}
\setlist[guidelines]{label={}, left=0pt .. \parindent, nosep}
\newlist{gwguidelines}{enumerate}{1}
\setlist[gwguidelines]{label={(\roman*)}, nosep}
\newlist{qparts}{enumerate}{2}
\setlist[qparts]{label={(\alph*)}}
\newlist{qsubparts}{enumerate}{2}
\setlist[qsubparts]{label={(\roman*)}}
\newlist{stmts}{enumerate}{1}
\setlist[stmts]{label={(\roman*)}, nosep}
\newlist{pflist}{itemize}{4}
\setlist[pflist]{label={$\bullet$}, nosep}
\newlist{enumpflist}{enumerate}{4}
\setlist[enumpflist]{label={(\arabic*)}, nosep}

\printanswers

\begin{document}
%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%
\title{EECS 203: Discrete Mathematics\\
  Winter 2024\\
  Assignment 0: Course Policies \& Page-Matching}
\date{}
\author{}
\maketitle
\vspace{-50pt}
\begin{center}
  \huge Due \textbf{THURSDAY, Jan. 18}, 10:00 pm\\
\Large No late homework accepted past midnight.\\
\vspace{10pt}
\large Number of Problems: 9
\hspace{3cm}
Total Points: 100
\end{center}
\vspace{25pt}
Like all future homeworks, this assignment should be submitted as a PDF through Gradescope (see instructions on course site for more details). We strongly prefer students to compose homework solutions using a word processor (Google Docs or MS Word), or ideally using \LaTeX, but we will accept handwritten homework submissions scanned/photographed and converted to PDF. Note that submitted files must be less than 50 mb in size, but they really should be much smaller than this. No email or Piazza regrade requests will be accepted. For more detail on regrade requests, please refer to course policies.

\begin{itemize}
    \item We will not grade homework problems that were not properly matched on Gradescope. Please submit early and often and double-check that you matched each question to the page(s) where your solution appears.
    \item Explanation or justification for yes/no, true/false, multiple choice questions, and the like: You must provide some sort of explanation or justification for these types of questions (so we know you didn’t just guess), unless explicitly specified in the problem statement. For example, simply answering “true” for a T/F question without providing an explanation will receive little or no credit.
    \item All problems require work to be shown. Questions that require a numerical answer will not be given credit if no work/explanation is shown.
    \item Honor Code: By submitting this homework, you agree that you are in compliance with the Engineering Honor Code and the Course Policies for 203, and that you are submitting your own work.
    \item Hyperlinks on Submitting Homework to Gradescope: \href{https://www.gradescope.com/help#help-center-item-student-submitting}{\textcolor{blue}{Instructions}} or
    \href{https://youtu.be/KMPoby5g_nE}{\textcolor{blue}{Youtube Video}}
\end{itemize}
\newpage

%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%

\subsection*{\probnum Did You Read The First Page? [6 points]}
Did you read the first page? We get it, it's a lot of words. Please give it a read! It's important information that you'll want to know as you complete homework assignments throughout the semester to \textbf{avoid losing points from logistical mistakes} \smiley{}. After you've given the first page a careful read over, write what you're most excited about in 2024 as your ``answer" to this question. 
\begin{solution}
\textbf{Grading Guidelines [6 points]}
\begin{guidelines}
    \item +6 any non-blank response
\end{guidelines}
\end{solution}

\subsection*{\probnum A Thing About Page Matching [6 points]}
You must match your pages to the problems on Gradescope in order to receive credit. Please note as soon as you press submit, you’ve successfully submitted by the deadline. You can still match the pages with no rush, that doesn’t add to your submission time. Write down your favorite class so far to affirm you've read and understand this.
\begin{solution}
\textbf{Grading Guidelines [6 points]}
\begin{guidelines}
    \item +6 any non-blank response
\end{guidelines}
\end{solution}


\subsection*{\probnum Resource Location [12 points]}
Where can you find each of the following resources? No justification necessary.
\begin{qparts}
    \item Lecture slides, lecture recordings, course announcements
    \item Scheduled office hours
    \item Questions and answers about course content and logistics (online forum)
\end{qparts}

\begin{solution}
\begin{qparts}
    \item Canvas
    \item Google calendar on Canvas
    \item Piazza
\end{qparts}

\textbf{Grading Guidelines [12 points]}

\textbf{For each part:}
\begin{guidelines}
    \item +4 correct answer
\end{guidelines}
\end{solution}


\subsection*{\probnum Exam dates [12 points]}
What are the dates and times of the three course exams? No justification necessary.

\begin{solution}
\begin{itemize}
    \item Exam 1: Monday, Feb 19, 7:00-9:00 PM
    \item Exam 2: Wednesday, Mar 27, 7:00-9:00 PM
    \item Exam 3: Tuesday, April 30, 7:00-9:00 PM
\end{itemize}

\textbf{Grading Guidelines [12 points]}

\textbf{For each exam:}
\begin{guidelines}
    \item +2 correct date (day of week not necessary)
    \item +2 correct time
\end{guidelines}
\end{solution}


\subsection*{\probnum Regrade Requests [16 points]}
\begin{qparts}
    \item Where do you submit a regrade request?
    
    \item What is the deadline for submitting regrade requests? Select \textbf{one} of the following:
    \begin{qsubparts}
        \item by the last day of classes
        \item by the next exam
        \item 24 hours after the assignment's grades have been released
        \item 1 week after the assignment's grades have been released
    \end{qsubparts}
    
    \item When should you submit a regrade request? Select \textbf{any number} of the following:
    \begin{qsubparts}
        \item I feel like I deserve more points
        \item My solution was incorrectly graded according to the posted rubric
        \item I have an alternate solution I think is right
        \item I have an alternate solution I think is right, and I checked it with an instructor in office hours or on Piazza
    \end{qsubparts}
    \item What 3 things should you make sure to (re)read before submitting a regrade request?
\end{qparts}

\begin{solution}
\begin{qparts}
    \item Gradescope
    \item (iv)
    \item (ii) and (iv)
    \item The posted solution, the rubric, and my solution
\end{qparts}

\textbf{Grading Guidelines [16 points]}

\textbf{For each part:}
\begin{guidelines}
    \item +4 correct answer
\end{guidelines}
\end{solution}

\subsection*{\probnum Admin Form [8 points]}
What is the best way to contact course staff about individual administrative concerns, and where can you find the link? 

\begin{solution}
The admin form. The link can be found on the homepage/syllabus of the course canvas page.

\textbf{Grading Guidelines [8 points]}
\begin{guidelines}
    \item +8 correct answer
\end{guidelines}
\end{solution}


\subsection*{\probnum Reflection [8 points]}
What strengths, strategies, and resources do you have to help you succeed in each of following?

\begin{qparts}
    \item Weekly assignments
    \item Exams
\end{qparts}

\begin{solution}
\begin{qparts}
    \item Strengths include any existing math or time management skills. Strategies include starting early, looking over discussion problems and solutions, and seeking help when you need it. Resources include classmates, office hours, Piazza, and regular attendance in lecture and discussion
    \item Strengths include study skills and test-taking strategies. Strategies include studying a little bit each day over a longer period of time, doing practice exams in a realistic exam setting, and getting a good night's sleep before the exam. Resources include review sessions, practice exams, problem roulette, office hours, Piazza, and regular attendance in lecture and discussion
\end{qparts}

\textbf{Grading Guidelines [8 points]}

\textbf{For each part:}
\begin{guidelines}
    \item +4 any non-blank response
\end{guidelines}
\end{solution}


\subsection*{\probnum Exponents [16 points]}
Compute the value of each of the following.  We encourage you to keep it in exponential form as long as you can, for practice. \textbf{Remember to show your work.}
\begin{qparts}
    \item $5^3$
    \item $2^3\cdot 2^2$
    \item $\frac{3^6}{3^3}$
    \item $5^0$
    \item $(2^4)^2$
    \item $2^{(4^2)}$ (use a calculator for this one if you need to!)
    \item $16^{\frac 12}$
    \item $16^{-2}$
\end{qparts}
\begin{solution}
\begin{qparts}
    \item $5^3=5\cdot5\cdot 5=125$
    \item $2^3\cdot 2^2=2^{3+2}=2^5=32$
    \item $\frac{3^6}{3^3}=3^{6-3}=3^3=27$
    \item $5^0=1$, since any non-zero number to the power of $0$ is $1.$
    \item $(2^4)^2=2^{4\cdot 2}=2^8=256$
    \item $2^{(4^2)}=2^{16}=65536$
    \item $16^{\frac 12}=\sqrt{16}=4$
    \item $16^{-2}=\frac 1{{16}^2}=\frac 1{256}$
\end{qparts}
\textbf{Grading Guidelines [16 points]}

\textbf{For each part:}
\begin{guidelines}
    \item $+1$ correct answer
    \item $+1$ shows work for computation
\end{guidelines}
\end{solution}

\subsection*{\probnum Logarithms [16 points]}
Compute the value of each of the following.  If the answer does not come out cleanly and results in an infinite decimal expansion, write ``\textit{too hard to compute}." If the result is not defined, write ``\textit{undefined}." For any question referencing $x$ or $y,$ let $\log_5(x)=2.6$ and $\log_5(y)=5.2.$ \textbf{Remember to show your work.}
\begin{qparts}
    \item $\log_2{64}$
    \item $\log_7{7}$
    \item $\log_7{1}$
    \item $\log_7{0}$
    \item $\log_5(x+y)$
    \item $\log_5(xy)$
    \item $\log_2(x)$
    \item $\log_5(x^{25})$
\end{qparts}

\begin{solution}
\begin{qparts}
    \item $2^6=64$, so $\log_2{64}=6$
    \item $7^1=7$, so $\log_7{7}=1$
    \item $7^0=1$, so $\log_7{1}=0$
    \item For any real number $c$, $7^c>0$, so we will never have $7^c=0$.  This means $\log_7{0}$ is undefined.
    \item A log of a sum does not come out to anything nice looking.  Too hard to compute.
    \item $\log_5(xy)=\log_5(x)+ \log_5(y)=2.6+5.2=7.8$
    \item A log of a different base would require a change of base formula:
    $$\log_2(x)=\frac{\log_b(x)}{\log_b(2)}$$
    for any base $b>0$ that we want. We know $\log_5(x)$, so let's let $b=5.$ We now have    $$\log_2(x)=\frac{\log_5(x)}{\log_5(2)}=\frac{2.6}{\log_5(2)}.$$  $\log_5(2)$, however, is not a clean number at all, so this is too hard to compute.
    \item $\log_5(x^{25})=25\log_5(x)=25\cdot 2.6=65$
\end{qparts}
\textbf{Grading Guidelines [16 points]}

\textbf{For each part:}
\begin{guidelines}
    \item $+1$ correct answer
    \item $+1$ correct justification/work shown
\end{guidelines}
\end{solution}

\end{document}
